---
title: "Delhi Environmental Sample Analysis"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#install.packages("pacman") # to install pacman if not already installed.
# import these packages using pacman
pacman::p_load(dplyr,ggplot2,hrbrthemes,ggpubr,readxl)
```

# 1.0 Import data

Read in the data from the excel file and print the first 6 rows using head()

```{r}
df <- readxl::read_excel(path = "../data/Environmental_Samples_Data_Jemma.xlsx",sheet = "Raw Data",skip = 5) %>% janitor::clean_names()
df %>% head()
```

## 2.1 Initial analysis

How many 0 values does each site have. It dictates how we plot the values further down. Log transforming the axis to make things readable means that we will remove all the 0 values.

```{r zeros}
df %>% 
  filter(cfu_ml==0) %>% 
  group_by(sample_type) %>% 
  tally()

```

Some summary statistics for the sample types - this creates a table of values.

```{r initial analysis}
df %>% 
  group_by(sample_type) %>% 
  summarise(Mean=mean(cfu_ml),Median=median(cfu_ml),SD=sd(cfu_ml))
```

## 2.2 Some initial plots

```{r exploratory plots}

# plot of cfu_ml by sample type and fill by site
df %>% 
  ggplot()+
  geom_violin(aes(x=sample_type,y=cfu_ml,fill=site),draw_quantiles = c(0.25,.5,.75),show.legend = FALSE)+
  geom_jitter(aes(x=sample_type,y=cfu_ml),alpha=0.2)+
  scale_y_continuous(trans="log10")+
  scale_fill_brewer(palette = "Pastel1")+
  scale_x_discrete(guide = guide_axis(angle=90))+
  facet_grid(~site,scale="free_x")+
  hrbrthemes::theme_ipsum()+
  xlab("Sample")+
  ylab("CFU per ml [log scale]")

```

### 2.1.1 Distal vs proximal samples.

```{r distal vs proximal}
# Only porximal/distal 
df %>% 
  filter(proximal_distal!="NA") %>% 
  ggplot()+
  geom_violin(aes(x=sample_type,y=cfu_ml,fill=site),draw_quantiles = c(0.25,.5,.75),show.legend = TRUE)+
  scale_y_continuous(trans="log10")+
  scale_fill_brewer(palette = "Pastel1")+
  scale_x_discrete(guide = guide_axis(angle=90))+
  facet_grid(~proximal_distal,scale="free_x")+
  hrbrthemes::theme_ipsum()+ 
  xlab("Sample")+
  ylab("CFU per ml [log scale]") #->b

#ggarrange(a,b,ncol= 2,labels = "auto")
```

## 3.0 Statistical analysis

$H_0$: there is a difference between prominal vs distal samples. We need to aggree on how to deal with censoring as the we get 

```{r stat analysis}
t.test(data=df %>% filter(proximal_distal!="NA" & cfu_ml>0),log10(cfu_ml)~proximal_distal) 
```

```{r}

```

